---
title: "Readme"
author: "Diego Alburez"
date: "1 7 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=TRUE)
```

[DEPRECATED: moved to general readme file]

Estimates mean number of months spent sandwiched (one value per country-cohort).

## Parallelisation

Works in Hydra (windows), should work in Linux.
Paralelises with dopar and it is quite fast and doesn't use that much memory (1 hr per menu item). 
Can run multiple jobs in Hydra

## Menu

Note that the estiamtes include sandwich and grandsandwich so no need to run separately!

Types of sandwich are:

```{r}
menu_choice <- "small_affinal"
menu_choice <- "medium_affinal"
menu_choice <- "medium_blood"
```


Other exist but are not essential.

```{r}

if(menu_choice == "small_affinal"){
  tau <- 5
  kappa_kids <- 5
  kappa_gkids <- 5
  cohorts_to_keep <- "every_5"
  include_in_laws <- T
  sex_keep <-  "both"  
} else if(menu_choice == "medium_affinal"){
  tau <- 5
  kappa_kids <- 15
  kappa_gkids <- 15
  cohorts_to_keep <- "every_5"
  include_in_laws <- T
  sex_keep <-  "both"    
} else if(menu_choice == "large_affinal"){
  tau <- 5
  kappa_kids <- 18
  kappa_gkids <- 18
  cohorts_to_keep <- "every_5"
  include_in_laws <- T
  sex_keep <-  "both"  
} else if(menu_choice == "medium_blood"){
  tau <- 5
  kappa_kids <- 15
  kappa_gkids <- 15
  cohorts_to_keep <- "every_5"
  include_in_laws <- F
  sex_keep <-  "both"    
} 
```

## Output (value)

On-the-go values are stores in a temp folder in ` ../../Data/temp`, which is defined according to the paramters provided:

```{r}
pat <- paste0(sex_keep, "_", cohorts_labs, "_", in_law_lab, "_k_s_", kappa_kids, "_k_gs_", kappa_gkids, "_", tau)
```

If the directory does not exist, it is created. 

## Todo

- Do age-specific values
- Figure out how to debug, eg. 001 Rsaves is not exported: Error in { : task 24 failed - "dim(X) muss positive Länge haben"
[1] "something screwed up in XIMS i= 1 ../../Data/temp/both_cohort_every_5_blood_kin_k_s_15_k_gs_15_5/001.Rsave Not written" 