---
title: "README: Bulk estimates of age-specific squeeze"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=TRUE)
```


[DEPRECATED: created higher-level readme one level up]
Last updated: 20200826

Run these scripts as an Rstudio JOB using the job_sandwich_regions.R file or similar.
This will estimate *sandwichness by age for all world countries saving a csv file for each country after it is processed.
This is, for each birth cohort, the share of a given age group that was (grand)sandwiched between generations.
Countries are ordered by regions (in the job file, there is a loop so that all countries are run by their regions only once)


## Parallelisation

Works in Hydra (windows) but will gve errors in Linux (mosty related to text format of country names, I think)
Written to run on Hydra 1 and 2 simulatenaous. 
The idea is to run 4 separate jobs from Rstudio using the corresponding scripts in this directory. 
For a two-sex population running on many cores, this takes around 2.5 days to run for each type of generational squeeze if you consider all cohort (see below).
Recommendation: estimate only evet 5 birth cohort year.

How to run:

1. Open the directory's Rstudio project
1. Open `00_run_jobs.R` and decide which jobs to run. If using the everz?5 cohorts onlz, zou can run everzthing in Hzdra 2 and it takes about 5 hours per region. Otherwise, use in Hydra 1 and 2. Normally, you would run, for example, sandwich job 1-2 in Hydra 1 and sandwich jobs 3-4 in Hydra 2. Don't run more than two jobs at the same time in each Hydra. Hydra 2 is faster and regions 3-4 take longer, so run them there.
1. After running all the jobs, run the `05_format_estimates.R` script to consolidate all the country-level results into a single csv file and export it to `Data/estimates`.

## Key parameters 

Thinks you might want to change for each type of estimate (see Output section):

### Type of generational squeeze

```{r}
type <- "sandwich"
# type <- "grandsandwich"
```

### Birth cohorts to keep:

By default, only works on 1970-2040 cohorts, the ones that makes sense to analyze.

`every_5` is prefered as running all cohorts takes around 3 days running 8 parallel jobs on both Hydras.

```{r}
cohorts_to_keep <- "every_5"
# cohorts_to_keep <- "all"

cohorts_labs <- paste0("cohort_", cohorts_to_keep)
```

### Definition of dependent child or grandchild:

As of June 29 2020, I am using the following definitions:

```{r}
kappa <- switch(type, sandwich = 18, grandsandwich = 15)
```

### Definition of dependent parent (years till death):

```{r}
tau <- 5
```

### Add in-laws?

Include parents-in-law within tau years of death, in addition to parents?
Note that this will chose fathers and mothers in law, irrespective of the value of `sex_keep`/

```{r}
in_laws <- TRUE

# For exporting name
in_law_lab <- ifelse(in_laws, "in_laws", "blood_kin")
```

### COnsider an all-female, all-male or mixed-sex population?

Keep only female, only male, or all types of kin?
In practice, it only determines the sex of egos and whether fathers, mothers, etc are chosen.
Children and in-lawas of both sexes are always considered.

```{r}
sex_keep <-  "both"
```

## Combination of parameters

For the final results, not all combination of parameters are needed. 
Here, I define the combinations that must be run to produce the desired results
Grandsandwich are the same parameters for each type.

The types of sandwiches available are:

```{r}
# This will determine which parameters are chosen for each type of 
# generational squeeze. Depending on the choice of sandwich, 
# the parameters.r script assigns the corresponding values.
# Note that the super-asssignemtn operator is required if running
# this from job scripts <<-

# Sandwich
menu_choice <- "sand_full"
# menu_choice <<- "sand_blood"
# menu_choice <<- "sand_female"

# Grandsandwich
# menu_choice <- "gsand_full"
# menu_choice <<- "gsand_blood"
# menu_choice <<- "gsand_female"
```

### FUll sandwich

```{r}
if(menu_choice == "sand_full"){
  type <- "sandwich"
cohorts_to_keep <- "every_5"
kappa <- switch(type, sandwich = 18, grandsandwich = 15)
tau = 5
in_laws <- TRUE
sex_keep <-  "both"
}

```

### Medium sandwich

```{r}
if(menu_choice == "sand_medium") {
  type <- "sandwich"
  cohorts_to_keep <- "every_5"
  kappa <- switch(type, sandwich = 15, grandsandwich = 15)
  tau = 5
  in_laws <- TRUE
  sex_keep <-  "both"
}
```

### Blood sandwich

Same as full sandwich, but ignores in-laws.

```{r}

if(menu_choice == "sand_blood"){

  type <- "sandwich"
  cohorts_to_keep <- "every_5"
  kappa <- switch(type, sandwich = 18, grandsandwich = 15)
  tau = 5
  in_laws <- F
  sex_keep <-  "both"
}

```

### Female sandwich

For comparing to formal model.

```{r}
if(menu_choice == "gsand_female"){
  
  type <- "sandwich"
cohorts_to_keep <- "every_5"
kappa <- switch(type, sandwich = 18, grandsandwich = 15)
tau = 5
in_laws <- T
sex_keep <-  "women"
}
```

### FUll grand-sandwich


```{r}
if(menu_choice == "gsand_full"){
  type <- "sandwich"
cohorts_to_keep <- "every_5"
kappa <- switch(type, sandwich = 18, grandsandwich = 15)
tau = 5
in_laws <- TRUE
sex_keep <-  "both"
}

```

### Blood grand-sandwich

Same as full sandwich, but ignores in-laws.

```{r}

if(menu_choice == "gsand_blood"){

  type <- "grandsandwich"
  cohorts_to_keep <- "every_5"
  kappa <- switch(type, sandwich = 18, grandsandwich = 15)
  tau = 5
  in_laws <- F
  sex_keep <-  "both"
}

```

### Female grand-sandwich

For comparing to formal model.

```{r}
if(menu_choice == "gsand_female"){
  
  type <- "grandsandwich"
cohorts_to_keep <- "every_5"
kappa <- switch(type, sandwich = 18, grandsandwich = 15)
tau = 5
in_laws <- T
sex_keep <-  "women"
}


```


## Input

A set of SOCSIM rsaves. The script actually works with csv files computed from Rsaves (which is not very efficient, but well...)
The input csv files are created by another job script (job_unpack.R) but this only needs to be done once (given a set of .rsaves files exported from SOCSIM).

## Output (value)

`05_format_estimates` should produce a 'full' and 'aggregate' csv file, each of which summarises, for each birth cohort, the share of a given age group that was squeezed between generations. 
The 'full' version includes estimates from multiple simulations while the aggregated one reports the mean of all simulations for each country.
Different definitions of squeeze are considered, producing a differen output each (and must be run seaprately).
You can identify what wach output csv files referes to by considering its name according to formula:

```{r}
print(paste0("~Data/estimates/socsim_", type,"_", sex_keep, "_", cohorts_labs, "_", in_law_lab, "_", kappa, "_", tau, "_", "full.csv"))
```

In addition, outputs to full estiamtes for each country in individual csv files (not aggregated in any way).

## Todo (20200629)

- Time sandwiched and grandsandwiched
- Save csv with menu_choice name only?
- Create Obj list to store all parameters for passing to functions instead of saving them in separate variables
- By 20200630, the files "socsim_sandwich_both_cohort_all_in_laws_18_5_aggregate" and "socsim_sandwich_both_in_laws_18_5_Albania" have the same type of information, but the coutnry-specific ones do not have the full name
- Countries within each region are not processed aphabetically - check that there's no error...
- Estimate duration 15_5